Histogram on Recent Runs by EMPv5

### 2017-02-23 pt_characterization/recent_data/paper.tex
characterizing draft

\begin{document}
\title{Empirical Check of Machine Homogeneity on Timing Protocol}

@@

\section{Description}
In this work we do a check to see if the result on the same experiment is different 
on different nodes, each with the same machine specification.

\section{Experiment Notes}
We provide a short description of our experimental runs. 
In these experiments we used four nodes ({\tt sodb8}, {\tt sodb9}, {\tt sodb10}, and {\tt sodb12} ) 
in the same cluster.

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3cm}|p{6cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
{\tt sodb8} &  INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb9} &  INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb10} & INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb12} & INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of INC data used for histograms\label{tab:exp_notes}}
\end{table}

\paragraph{Measurement Quality Across the SoDB Nodes:} 
Fig.~\ref{fig:machine_comp} shows 
the standard deviation and relative error of 
elapsed time (ET) and process time (PT) on the different SoDB nodes 
as the task length of INC increases.

\begin{figure}[t]
	\centering
	\subfigure[Standard Deviation - ET]{
		\includegraphics[scale=0.6]{overall/machine_et_std.eps}
        \label{fig:pt_std}
    }
    \subfigure[Relative Error - ET]{
        \includegraphics[scale=0.6]{overall/machine_et_re.eps}
        \label{fig:pt_re}
    }
	\subfigure[Standard Deviation - PT]{
		\includegraphics[scale=0.6]{overall/machine_pt_std.eps}
        \label{fig:pt_std}
    }
    \subfigure[Relative Error - PT]{
        \includegraphics[scale=0.6]{overall/machine_pt_re.eps}
        \label{fig:pt_re}
    }
    \caption{Measurement Quality Comparison among Different SoDB Machines}
    \label{fig:machine_comp}
\end{figure}

@@

Each of the following sections exhibits histograms of ET and PT 
over increasing INC's task lengths on each individual node.

\input{sodb8/res.tex}
\input{sodb9/res.tex}
\input{sodb10/res.tex}
\input{sodb12/res.tex}

\section{Conclusion}
My recommendation is to avoid {\tt sodb8} and to use the rest of 
the SoDB nodes for the rest of our experiments. Further investigation is 
needed to examine why the experiment results on {\tt sodb8} are different 
than those of the other nodes.

>>>>

\begin{document}
\title{Histogram on Recent Runs by EMPv5}

@@

\section{Description}
This document presents histograms based on the most recent runs 
of a program under test, called {\em INC}, over its increasing task lengths.

\section{Experiment Notes}
Table~\ref{tab:exp_notes} provides a short description of our experimental runs, 
on which the following histograms are based.

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3cm}|p{6cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
{\tt sodb9} &  INC1$\sim$INC1024 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10 / 2017-02-12 $\sim$ 2017-02-19\\ \hline
{\tt sodb10} & INC2048 & Runs of 300 samples & 2017-02-12 $\sim$ 2017-02-20\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of INC data used for histograms\label{tab:exp_notes}}
\end{table}

Now we show histograms of elapsed time (ET) and process time (PT) 
over increasing INC's task lengths.

@@

\input{sodb9/res.tex}

### 2017-02-23 pt_characterization/recent_data/sodb9/res.tex
characterizing draft

\section{{\tt sodb9}~\label{sec:sodb9_hist}} 
This section exhibits histograms on the EMPv5 data obtained on {\tt sodb9}. 
The detailed description of the base data are from Table~\ref{tab:exp_notes}.

@@

@@

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC16]{
		\includegraphics[scale=0.43]{sodb9/16_sec_pt_hist_v5.eps}
		\label{fig:inc16_hist_v5}
	}
	\subfigure[PT frequency on INC32]{
		\includegraphics[scale=0.43]{sodb9/32_sec_pt_hist_v5.eps}
		\label{fig:inc32_hist_v5}
	}
	\subfigure[PT frequency on INC64]{
		\includegraphics[scale=0.43]{sodb9/64_sec_pt_hist_v5.eps}
		\label{fig:inc64_hist_v5}
	}
	\subfigure[PT frequency on INC128]{
		\includegraphics[scale=0.43]{sodb9/128_sec_pt_hist_v5.eps}
		\label{fig:inc128_hist_v5}
	}
	\caption{PT Histograms of INC16 ... INC64~\label{fig:s9_pt_hist2}}
\end{figure}

>>>>

\section{Histograms~\label{sec:sodb9_hist}} 
This section exhibits histograms on the EMPv5 data obtained when 
the task length of INC increases from 1 second to 2048 seconds. 
The detailed description of the base data are from Table~\ref{tab:exp_notes}.

@@

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC256]{
		\includegraphics[scale=0.43]{sodb9/256_sec_et_hist_v5.eps}
		\label{fig:inc256_hist_v5}
	}
	\subfigure[ET frequency on INC512]{
		\includegraphics[scale=0.43]{sodb9/512_sec_et_hist_v5.eps}
		\label{fig:inc512_hist_v5}
	}
	\subfigure[ET frequency on INC1024]{
		\includegraphics[scale=0.43]{sodb9/1024_sec_et_hist_v5.eps}
		\label{fig:inc1024_hist_v5}
	}
	\subfigure[ET frequency on INC2048]{
		\includegraphics[scale=0.43]{sodb10/2048_sec_et_hist_v5.eps}
		\label{fig:inc2048_hist_v5}
	}
	\caption{ET Histograms of INC256 ... INC2048~\label{fig:s9_et_hist3}}
\end{figure}

@@

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC16]{
		\includegraphics[scale=0.43]{sodb9/16_sec_pt_hist_v5.eps}
		\label{fig:inc16_hist_v5}
	}
	\subfigure[PT frequency on INC32]{
		\includegraphics[scale=0.43]{sodb9/32_sec_pt_hist_v5.eps}
		\label{fig:inc32_hist_v5}
	}
	\subfigure[PT frequency on INC64]{
		\includegraphics[scale=0.43]{sodb9/64_sec_pt_hist_v5.eps}
		\label{fig:inc64_hist_v5}
	}
	\subfigure[PT frequency on INC128]{
		\includegraphics[scale=0.43]{sodb9/128_sec_pt_hist_v5.eps}
		\label{fig:inc128_hist_v5}
	}
	\caption{PT Histograms of INC16 ... INC128~\label{fig:s9_pt_hist2}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC256]{
		\includegraphics[scale=0.43]{sodb9/256_sec_pt_hist_v5.eps}
		\label{fig:inc256_hist_v5}
	}
	\subfigure[PT frequency on INC512]{
		\includegraphics[scale=0.43]{sodb9/512_sec_pt_hist_v5.eps}
		\label{fig:inc512_hist_v5}
	}
	\subfigure[PT frequency on INC1024]{
		\includegraphics[scale=0.43]{sodb9/1024_sec_pt_hist_v5.eps}
		\label{fig:inc1024_hist_v5}
	}
	\subfigure[PT frequency on INC2048]{
		\includegraphics[scale=0.43]{sodb10/2048_sec_pt_hist_v5.eps}
		\label{fig:inc2048_hist_v5}
	}
	\caption{PT Histograms of INC256 ... INC2048~\label{fig:s9_pt_hist3}}
\end{figure}
